%-------------------------
% Resume in Latex
% Based off of: https://github.com/sb2nov/resume
% and Jake Gutierrez's version of it
% at https://www.overleaf.com/latex/templates/jakes-resume/syzfjbzwjncs
% inspired by https://practicaltypography.com/resumes.html
% License : MIT
%------------------------
% Set Arial as the main font for 
\documentclass[letterpaper,11pt]{article}
\usepackage{fontspec}  % Load the fontspec package which is essential for specifying fonts in XeLaTeX and LuaLaTeX
\setmainfont{Arial}    

\usepackage{tikz}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames, dvipsnames]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{wrapfig}
\usepackage{graphicx}
\usepackage[margin = 0.5 in]{geometry}
\usepackage{contour}
\usepackage{ulem}
\usepackage{fontawesome5}

%--------------UNDERLINING---------------
% taken from https://alexwlchan.net/2017/10/latex-underlines/

\renewcommand{\ULdepth}{3.8pt}
\contourlength{0.8pt}

\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}

%----------------------------------------

\graphicspath{ {./Images/} }

% Define a custom darker blue color
\definecolor{custommediumblue}{RGB}{0, 102, 204} % Adjust the RGB values for a medium shade

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.1in}
\addtolength{\marginparsep}{0.1in}
\addtolength{\evensidemargin}{-0.1in}
\addtolength{\textwidth}{0.2in}
\addtolength{\topmargin}{-0.1in}
\addtolength{\textheight}{0.5in}

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
% Define the title for the section with added space
 
% Ensure consistent titlespacing for all sections
\titlespacing*{\section}{0pt}{6pt}{2pt}  % Left margin is 0pt

% Ensure consistent section title format
\titleformat{\section}{
  \color{custommediumblue}\fontsize{12}{12}\selectfont\titlerule\vspace{0.5pt}
  \vspace{1 pt}\raggedright\bfseries
}{}{0pt}{}

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \small#3 & \small#4 \\
  \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in, label= • , topsep=2pt, itemsep=1pt, partopsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% ----------HEADING----------
{
    \color{custommediumblue}\large\fontsize{20pt}{20pt}\selectfont\bfseries\raggedright Hamideh Shahrabi 
    
    }
    
    \href{mailto:shahrabh@mcmaster.ca}{
        \faEnvelope
        \thinspace \thinspace
        \myuline{Hamideh.shahrabi88@gmail.com}} $|$
    \faPhone
    \thinspace \thinspace
    289-639-7574 $|$
    \href{https://www.linkedin.com/in/hamideh-shahrabi-75345553}{
        \faLinkedin
        \thinspace \thinspace        
        \myuline{LinkedIn}} $|$
    \href{https://github.com/hamideshahrabi/}{
        \faGithub
       \thinspace \thinspace
        \myuline{GitHub}}

%----------- Professional Summary -----------
\section{\textcolor{custommediumblue}{Professional Summary}}
\begin{itemize}[leftmargin=0.15in, label= • , topsep=-5pt, itemsep=0pt, partopsep=0pt]
   \small{

    Machine Learning Engineer with 5+ years of experience delivering end-to-end AI and data science solutions, including predictive modeling, statistical analysis, and large language model (LLM) development. Proficient in Python and SQL, with experience fine-tuning LLMs, crafting effective prompts, and building intelligent NLP systems such as summarization and question answering. Skilled in deploying models using GCP, Docker, and Kubernetes, and familiar with retrieval-augmented generation (RAG). Passionate about building responsible, high-impact AI applications that translate complex research into real-world value.


   }
\end{itemize}

%-----------Technical Skills-----------
\section{\textcolor{custommediumblue}{Technical Skills}}
\resumeSubHeadingListStart
\begin{itemize}[leftmargin=0.15in, label= • , topsep=-5pt, itemsep=0pt, partopsep=0pt]
    \small{
    \item\textbf{Programming Languages:} Python, SQL
    
    \item\textbf{ML \& Deep Learning:} Transformers, fine-tuning, prompt engineering, TensorFlow, PyTorch, Keras, scikit-learn, XGBoost
    
    \item\textbf{LLM Tools:} GPT-3.5, GPT-4, Gemini, Gemini Pro, Claude, Flan-T5, LangChain, RAG, LlamaIndex, Hugging Face Transformers
    
    \item\textbf{Statistical \& Quantitative Techniques:} Regression models, A/B testing, model evaluation (RMSE, precision/recall), hypothesis testing
    
    \item\textbf{Data Processing:} Pandas, NumPy, ETL pipelines, Apache Spark
    
    \item\textbf{Cloud Platforms:} AWS (SageMaker, EC2, S3, Bedrock), GCP (Vertex AI, BigQuery), Azure, Databricks
    
    \item\textbf{Infrastructure \& DevOps:} CI/CD pipelines, REST API development, Docker, Kubernetes, Kubeflow, Git, MLflow
    
    \item\textbf{Visualization:} Plotly, Matplotlib, Seaborn
    }
\end{itemize}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{\textcolor{custommediumblue}{Professional Experience}}
\resumeSubHeadingListStart

\resumeSubheading
{Machine Learning Engineer}{Nov. 2024 -- Present}
{McMaster University, Hamilton, Canada}{}
\resumeItemListStart

\resumeItem{Enabled editorial teams to reduce content review time by 50\% by developing a custom LLM-powered assistant, streamlining editing and translation workflows for faster publishing.}

\resumeItem{Developed a full-stack LLM-powered editor (GPT-3.5, GPT-4, Gemini Pro) from scratch, streamlining content workflows — source code and demo available on GitHub.}
\resumeItem{Fine-tuned LLMs on domain-specific datasets, boosting output accuracy by 40\% and reducing repetitive manual cycles.}
\resumeItem{Engineered adaptive prompt templates with role-based conditioning and smart token-efficient routing to support agentic AI use cases.}
\resumeItem{Designed and deployed an LLM-powered assistant for real-time editing and translation support, reducing manual intervention by 50\% and improving user-facing content workflows.}
\resumeItem{Developed a custom user interface for an LLM-powered editing platform, enabling live side-by-side comparisons and improving user interaction through intuitive design.}
\resumeItem{Collaborated closely with business partners and external stakeholders, translating technical goals into tailored LLM solutions for content creation workflows.}
\resumeItemListEnd

\resumeSubheading
{Machine Learning Engineer}{Dec. 2023 -- Oct. 2024}
{Electrical Power Engineers (EPE), Toronto, Canada}{}
\resumeItemListStart
\resumeItem{Automated over 70\% of user queries with a custom-built chatbot, freeing up manual support resources and improving customer response time significantly.}
    
\resumeItem{Built and deployed an AI chatbot using GPT-3.5 and Flan-T5 to handle user queries, automating repetitive communication tasks.}
\resumeItem{Transformed static data into dynamic dashboards using Plotly, supporting faster insight generation.}
%\resumeItem{Integrated models with RESTful APIs and deployed using CI/CD pipelines on AWS and GCP.}

 \resumeItem{ Deployed scalable ML solutions in cloud environments (AWS/GCP) using Docker and Kubernetes for containerization and orchestration.}
\resumeItem{Served as a technical liaison during collaborative sessions with cross-functional teams and end users, ensuring ML outputs aligned with business needs in a consultative capacity.}
\resumeItem{Led technical discussions and provided mentorship to junior contributors during chatbot development and model integration efforts.}
\resumeItemListEnd

\resumeSubheading
{Data Scientist}{Jul. 2021 -- Nov. 2023}
{Tejarat Gostar}{}
\resumeItemListStart
\resumeItem{Improved product recommendation accuracy and boosted customer retention by 15\% through predictive modeling and user behavior segmentation.}
\resumeItem{Reduced data processing time by 30\% through SQL query optimization.}
%\resumeItem{Developed and deployed ML models for customer behavior modeling and demand forecasting.}
\resumeItem{Delivered automated reporting tools to track performance metrics and drive decision-making.}
\resumeItem{Worked cross-functionally to translate analytics into actionable product insights.}
\resumeItem{Analyzed product and user data to support predictive modeling and improve business decision-making.}
%\resumeItem{Performed statistical tests (e.g., hypothesis testing, confidence intervals) to support data-driven decisions across departments.}
\resumeItemListEnd

\resumeSubheading
{Software Engineer}{Apr. 2020 -- Apr. 2021}
{MojeNovin}{}
\resumeItemListStart
\resumeItem{Designed RESTful APIs using FastAPI and built full-stack applications to support editorial teams.}
\resumeItem{Enhanced MySQL performance by 25\% through schema optimization and indexing.}
\resumeItem{Developed responsive web interfaces, increasing front-end usability and user engagement.}
\resumeItem{Used Git and GitHub for collaborative version control and CI integration.}
\resumeItem{Built internal dashboards to streamline team operations and increase delivery speed.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{\textcolor{custommediumblue}{Education}}
\resumeSubHeadingListStart

\resumeSubheading
{Master of Engineering, Systems and Technology Engineering}{2023 -- 2024}
{McMaster University, Hamilton, Canada}{}

\resumeSubheading
{Master of Engineering, Computer Engineering}{}
{Shahid Beheshti University}{}

\resumeSubheading
{Bachelor of Science, Computer Engineering}{}
{Islamic Azad University}{}

\resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{\textcolor{custommediumblue}{Licenses \& Certifications}}
\resumeSubHeadingListStart
\begin{itemize}[leftmargin=0.15in, label= • , topsep=-5pt, itemsep=0pt, partopsep=0pt]
    \small{
    % AI/ML Certificates
    \item \textbf{AWS Educate} - Introduction to Generative Artificial Intelligence (Mar. 2024)
    \item \textbf{The Linux Foundation} - PyTorch and Deep Learning for Decision Makers (LFS116) (Feb. 2024)
    
    % DevOps/Infrastructure Certificates
    \item \textbf{The Linux Foundation} - Introduction to Kubernetes (LFS158) (Jan. 2024)
    \item \textbf{LinkedIn Learning} - Learning GitHub Actions (Jan. 2024)
    \item \textbf{LinkedIn Learning} - Continuous Integration and Continuous Delivery with GitLab (Dec. 2023)
    \item \textbf{LinkedIn Learning} - Learning GitLab (Dec. 2023)
    }
\end{itemize}
\resumeSubHeadingListEnd

\end{document} 